\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-10-01 Documents/M1/Astronum_2018/manuscript.tex
Comments on paper
Backup once more.
Added abstract.

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\usepackage{./definitions}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}

@@

\begin{document}
\title{\texttt{thornado}-transport: a realizability-preserving IMEX scheme for two-moment neutrino transport}

@@

\author{Eirik Endeve}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\ead{endevee@ornl.gov}

\author{Cory D. Hauck}
\address{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\ead{hauckc@ornl.gov}

@@

\author{Bronson Messer}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\address{Scientific Computing and Theoretical Physics Groups, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
%\address{Physics Division, Oak Ridge National Laboratory, P.O. Box 2008, Oak Ridge, TN 37831-6354, USA}
\ead{bronson@ornl.gov}

\begin{abstract}
All articles {\it must} contain an abstract...
\end{abstract}

>>>>

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\usepackage{./definitions}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{url}

\newcommand{\ee}[1]{{\color{red} EE:~#1}}
\newcommand{\rc}[1]{{\color{blue} RC:~#1}}

@@

\begin{document}
\title{\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics}

@@

\author{Eirik Endeve}
\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\ead{endevee@ornl.gov}

\author{Cory D. Hauck}
\address{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\address{Department of Mathematics, University of Tennessee Knoxville, TN 37996-1320}
\ead{hauckc@ornl.gov}

@@

\author{Bronson Messer}
\address{Scientific Computing and Theoretical Physics Groups, Oak Ridge National Laboratory, Oak Ridge, TN 37831 USA}
\address{Department of Physics and Astronomy, University of Tennessee Knoxville, TN 37996-1200}
\ead{bronson@ornl.gov}

\begin{abstract}
We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method.
Two-moment method evolves the angular moments of a neutrino phase space distribution function and the moments have upper and lower bounds that introduced by Pauli's exclusion principle.
To ensure the scheme preserves these bounds, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure which preserves the bounds is chosen for our IMEX schemes.
For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_2018}.
PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
The two PD-ARSs have second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore second-order and third-order accurate in the streaming limit.
The accuracy and convex-variance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.

\end{abstract}
